### 2025-04-08 correlation.qmd
20250407 - fix error

The $r$ value (`{r} petersenlab::apa(pearson_r, digits = 2)`) is slightly negative.
The [effect size](#sec-practicalSignificance) of the association is small—for what is considered a small, medium, and large effect size for $r$ values, see @sec-effectSizeThresholds.
The $p$-value is less than .05, so it is a statistically significant correlation.
We could report this finding as follows: There was a statistically significant, weak negative association between height and fantasy points ($r[$ `{r} pearson_df` $]=$ `{r} petersenlab::apa(pearson_r, digits = 2)`, $p < .001$); the taller a player was, the fewer fantasy points they tended to score.

>>>>

The $r$ value (`{r} petersenlab::apa(pearson_r, decimals = 2)`) is slightly negative.
The [effect size](#sec-practicalSignificance) of the association is small—for what is considered a small, medium, and large effect size for $r$ values, see @sec-effectSizeThresholds.
The $p$-value is less than .05, so it is a statistically significant correlation.
We could report this finding as follows: There was a statistically significant, weak negative association between height and fantasy points ($r[$ `{r} pearson_df` $]=$ `{r} petersenlab::apa(pearson_r, decimals = 2)`, $p < .001$); the taller a player was, the fewer fantasy points they tended to score.
